Convex Surrogates via Polyhedral Losses

### 2019-02-02 cvx-fin.tex
tweaks

\subsection{Notation}
\begin{itemize}
  \item $\Y$ is the finite outcome space, and $n := |\Y|$.
  \item $\simplex\subseteq\reals^\Y$ is the set of distributions over $\Y$, thought of as vectors of probabilities.
  \item For an outcome $y$, we denote $p_y$ as the probability of outcome $y$ being observed in nature.
  \item If $\gamma = \prop{\ell}$, then $\gamma:\simplex \toto \R$ is the property elicited by the loss $\ell: \R \to \reals^\Y$.
  \item $d$ is the dimension of the embedding space
  \item $L:\reals^d \to \reals^\Y_+$ is a loss taking a report $u \in \reals^d$ and mapping the loss over each outcome in $\Y$. \raf{Changed to $\reals^\Y_+$ below.}
  \item $\Gamma: \simplex \toto \reals^d$ is the set-valued property mapping a probability distribution to a report $u \in \reals^d$.
  \item $\Gamma_u = \{ p \in \simplex : u \in \Gamma(p) \}$
  \item $\psi$ is the link function (see below)
  \item $\varphi:\R \to \reals^d$ is the embedding function
  \item $\trim(\Gamma)$ and $\strip(\Gamma)$
  \item $\eliccvx$, $\elicembed$, and $\elicpoly$
  \item $V$ and $B(P)$ as we get ready for later.
\end{itemize}

@@

Most of the loss functions $L$ we consider will be piecewise linear and convex, or \emph{polyhedral}; we therefore will make use of the theory of convex polytopes.
In $\reals^d$, a \emph{polyhedral set} or \emph{polyhedron} is the intersection of a finite number of halfspaces.
A \emph{polytope} is a bounded polyhedral set.
A convex function $f:\reals^d\to\reals$ is \emph{polyhedral} if its epigraph is polyhedral, or equivalently, if it can be written as a pointwise maximum of a finite set of affine functions~\cite{rockafellar1997convex}.

@@

When designing a surrogate loss function, we require some sort of statistical consistency with the original loss, so that minimizing the surrogate is an effective alternative to directly minimizing the original loss.
We formalize this consistency below in terms of the properties elicited by each loss.
In particular, we seek a \emph{link} function, which maps optimal reports from the surrogate to the original reports, satisfying certain guarantees.
\bo{Maybe mention that previous formalizations are for single-valued properties only if true? And if so, that they don't really apply to finite properties??}

@@

Roughly speaking, a calibrated link requires that optimal surrogate reports map to optimal original reports, while a separated link adds the stronger guarantee that one cannot approach the optimal surrogate loss while making suboptimal original predictions.
A classic example of a link which is both calibrated and separated is $\psi = \sgn$ when $\gamma=\mode$ and $L$ is either hinge loss or logistic loss.
On the other hand, the link $\psi(u) =
\begin{cases}
  -1 & u \leq -1\\
  1 & u > -1
\end{cases}$
would not be separated for hinge loss, but it would still be calibrated, as the reports $u\in(-1,1)$ are optimal for hinge loss only when $p=(1/2,1/2)$, in which case both $-1$ and $1$ are optimal for the mode (0-1 loss).

\raft{Aside about other link definitions commented out}
% As a brief aside, it is interesting to contrast the definitions above with the following: a link is
% \emph{exhaustive} if for all $p\in\simplex$, $\gamma(p) = \psi(\Gamma(p)) := \{\psi(r') : r'\in\Gamma(p)\}$.
% A \emph{strong link} is a set-valued function $\psi:\R'\toto\R$ such that for all $p\in\simplex$ and $r'\in\R'$, we have $r'\in\Gamma(p) \implies \gamma(p) = \psi(r')$.
% If sign is interpreted as set-valued (0 maps to $\{1,-1\}$, then it is strong for logistic.  If not, sign is not exhaustive for logistic.  Sign is exhaustive for hinge.}

It is often useful to express the relationship between $L$ and $\gamma$ above directly, which is the notion of \emph{indirect elicitation}.

@@

As a brief aside, we note that previous definitions of elicitation complexity have used a more straightforward link function, as the properties considered were single-valued~\citep{lambert2008eliciting,fissler2016higher,frongillo2015elicitation}.
In particular, if both $\gamma$ and $\Gamma$ are single-valued, these works simply require $\gamma = f \circ \Gamma$.
When $\Gamma$ is set-valued, one still straightforwardly requires $\gamma(p) = f(u)$ for all $u \in \Gamma(p)$.
The notion a calibrated link from Definition~\ref{def:links} is only required when both $\gamma$ and $\Gamma$ could be set-valued, as is the case in general for convex surrogates of finite properties.

>>>>

% \subsection{Notation}
% \begin{itemize}
%   \item $\Y$ is the finite outcome space, and $n := |\Y|$.
%   \item $\simplex\subseteq\reals^\Y$ is the set of distributions over $\Y$, thought of as vectors of probabilities.
%   \item For an outcome $y$, we denote $p_y$ as the probability of outcome $y$ being observed in nature.
%   \item If $\gamma = \prop{\ell}$, then $\gamma:\simplex \toto \R$ is the property elicited by the loss $\ell: \R \to \reals^\Y$.
%   \item $d$ is the dimension of the embedding space
%   \item $L:\reals^d \to \reals^\Y_+$ is a loss taking a report $u \in \reals^d$ and mapping the loss over each outcome in $\Y$. \raf{Changed to $\reals^\Y_+$ below.}
%   \item $\Gamma: \simplex \toto \reals^d$ is the set-valued property mapping a probability distribution to a report $u \in \reals^d$.
%   \item $\Gamma_u = \{ p \in \simplex : u \in \Gamma(p) \}$
%   \item $\psi$ is the link function (see below)
%   \item $\varphi:\R \to \reals^d$ is the embedding function
%   \item $\trim(\Gamma)$ and $\strip(\Gamma)$
%   \item $\eliccvx$, $\elicembed$, and $\elicpoly$
%   \item $V$ and $B(P)$ as we get ready for later.
% \end{itemize}

@@

Most of the loss functions $L$ we consider will be piecewise linear and convex, or \emph{polyhedral}; we therefore will make use of the theory of convex polytopes.
In $\reals^d$, a \emph{polyhedral set} or \emph{polyhedron} is the intersection of a finite number of halfspaces.
A \emph{polytope} is a bounded polyhedral set.
A convex function $f:\reals^d\to\reals$ is \emph{polyhedral} if its epigraph is polyhedral, or equivalently, if it can be written as a pointwise maximum of a finite set of affine functions~\citep{rockafellar1997convex}.

@@

When designing a surrogate loss function, we require some sort of statistical consistency with the original loss, so that minimizing the surrogate is an effective alternative to directly minimizing the original loss.
We formalize this consistency below in terms of the properties elicited by each loss.
In particular, we seek a \emph{link} function, which maps optimal reports from the surrogate to the original reports, satisfying certain guarantees.

@@

Roughly speaking, a calibrated link requires that optimal surrogate reports map to optimal original reports, while a separated link adds the stronger guarantee that one cannot approach the optimal surrogate loss while making suboptimal original predictions.
A classic example of a link which is both calibrated and separated is $\psi = \sgn$ when $\gamma=\mode$ and $L$ is either hinge loss or logistic loss.
On the other hand, the link $\psi(u) =
\begin{cases}
  -1 & u \leq -1\\
  1 & u > -1
\end{cases}$
would not be separated for hinge loss, but it would still be calibrated, as the reports $u\in(-1,1)$ are optimal for hinge loss only when $p=(1/2,1/2)$, in which case both $-1$ and $1$ are optimal for the mode (0-1 loss).
\raft{Aside about other link definitions commented out}
% As a brief aside, it is interesting to contrast the definitions above with the following: a link is
% \emph{exhaustive} if for all $p\in\simplex$, $\gamma(p) = \psi(\Gamma(p)) := \{\psi(r') : r'\in\Gamma(p)\}$.
% A \emph{strong link} is a set-valued function $\psi:\R'\toto\R$ such that for all $p\in\simplex$ and $r'\in\R'$, we have $r'\in\Gamma(p) \implies \gamma(p) = \psi(r')$.
% If sign is interpreted as set-valued (0 maps to $\{1,-1\}$, then it is strong for logistic.  If not, sign is not exhaustive for logistic.  Sign is exhaustive for hinge.}

It is often useful to express the relationship between $L$ and $\gamma$ without referring to $\Gamma=\prop{L}$, which is captured by \emph{indirect elicitation}.

@@

As a brief aside, we note that previous definitions of elicitation complexity have used a more straightforward link function, as the properties considered were single-valued~\citep{lambert2008eliciting,fissler2016higher,frongillo2015elicitation}.
In particular, if both $\gamma$ and $\Gamma$ are single-valued, these works simply require $\gamma = f \circ \Gamma$.
When $\Gamma$ is set-valued, one still straightforwardly requires $\gamma(p) = f(u)$ for all $u \in \Gamma(p)$.
The notion of a calibrated link from Definition~\ref{def:links} is only required when both $\gamma$ and $\Gamma$ could be set-valued, as is the case in general for convex surrogates of finite properties.
